\documentclass[a4paper,10pt]{letter}
\usepackage{hyperref}
\usepackage[a4paper]{geometry}
\geometry{top=2.5cm, bottom=2.5cm}



\date{February 25, 2021}

\signature{Agustina Pesce}

% \address{}

\begin{document}

\begin{letter}
{To whom it may concern / Dear Human Resources Team,}
\opening{}

I'm writing to express my interest in working with you in a position like the 
Data Scientist, Software Engineer or Web Developer.
I am applying to these positions due to my scientific and computer 
knowledge. 

I'm a Physicist and a PhD in Geophysics working on scientific research at
\href{https://www.conicet.gov.ar/}{CONICET}.
During my PhD and my postdoc I had the opportunity to learn and improve my
Python programming skills to process, visualize and analyze data. 

I'm also committed to contribute to open-source software projects to improve
science openness and reproducibility.
In this sense, I've made contributions to the libraries of the
\href{https://fatiando.org}{Fatiando a Terra} project (open-source tools for
geophysics) and lately to \href{https://github.com/ggciag/mandyoc}{Mandyoc}(a 
mantle dynamics simulator).
Moreover, I've started developing 
\href{https://github.com/aguspesce/tapioca}{tapIOca}, a set of Python tools to 
load, visualize and analyze the outputs of Mandyoc.

To satisfy my curiosity, I'm also learning about web design and development.
I collaborated to some project like 
\href{https://geolatinas.github.io/}{Geolatinas Coding group} and 
\href{https://www.fatiando.org/}{Fatiando main website}. 
I have also made designs of my own, like \href{https://dianaceroallard.github.io/}{Diana 
personal website}, \href{https://aguspesce.github.io/garabatos/}{Garabatos} and 
\href{https://aguspesce.github.io/web-cromografica/}{CromoGrafica}. 

Having a solid background in Physics provided a strong foundation for building 
my knowledge.
It allowed me to satisfy my curiosity and develop myself as a self-taught coder 
who enjoy learning new tools and improve my computer-science skills.
On the way I learned how to efficiently solve problems and apply the best
practices for software development.

I would like to thank you for taking the time to review my curriculum and 
consideration. 
I look forward to hearing about some employment opportunity.


\closing{Sincerely,}


\end{letter}
\end{document}
